PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
change external ref to login ID for RAMP

ramp.dem.raw$externalDataReference <- ramp.dem.raw$`Login ID` #move Login ID to external data reference

  ramp.dem.raw.id <- ramp.dem.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
#      startDate.coping, #Date when participant signed up to ramp  (is in the coping gad chunk)
      age_category_full = demographics.how_old_are_you, # Age
      Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
#     EduYrs = demographics.university_education_attend_school.txt, # Years in education - not in RAMP dataset
#     demographics.college_or_university_degree, # level of education - univeristy - level of education is in employment file
#     demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
#     demographics.o_levelsgcses_or_equivalent, # level of education - gcse
#     demographics.cses_or_equivalent, # level of education - cse
#     demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
      Transgender_uncleaned = demographics.do_you_identify_as_transgender,
      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
    ) %>%
    add_numeric(., exclude = exclude_cols_dem) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.employment.raw.id <- ramp.employment.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

>>>>

  ramp.dem.raw.id <- ramp.dem.raw %>%
    drop_na(`Login ID`) %>% # Drop NAs
    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
#      startDate.coping, #Date when participant signed up to ramp  (is in the coping gad chunk)
      age_category_full = demographics.how_old_are_you, # Age
      Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
#     EduYrs = demographics.university_education_attend_school.txt, # Years in education - not in RAMP dataset
#     demographics.college_or_university_degree, # level of education - univeristy - level of education is in employment file
#     demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
#     demographics.o_levelsgcses_or_equivalent, # level of education - gcse
#     demographics.cses_or_equivalent, # level of education - cse
#     demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
      Transgender_uncleaned = demographics.do_you_identify_as_transgender,
      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
    ) %>%
    add_numeric(., exclude = exclude_cols_dem) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.employment.raw.id <- ramp.employment.raw %>%
  drop_na('Login ID') %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
